Testing production scenarios for (anti-)(hyper-)nuclei with multiplicity-dependent measurements at the LHC

### 2019-03-31 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
Results part. Discussion and conclusions missing - sigh. I have to go for my lunch appointment ---will continue later.

\subsection{The coalescence approach}
In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963, Kapusta:1980, Scheibl:1998tk}.
The coalescence probability is encoded in the coalescence parameter, $B_{A}$.
Considering that at LHC energies the number of produced protons and neutrons at midrapidity as well as their momentum distributions are expected to be equal, $B_{A}$ is defined as
%
%
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p,n}}\frac{\mathrm{d}^{3}N_{\mathrm{p,n}}}{\mathrm{d}p_{\mathrm{p,n}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.,
\label{eq:BA}
\end{equation}
%
%
where $p_{\mathrm{p,n}}$ are the proton and neutron momenta and $E_{p,n}$ their energies. 
Equation~\ref{eq:BA} represents also the operative definition of $B_A$ that is used by experiments like ALICE to extract the coalescence probability starting from the measured nucleus and nucleon (proton) distributions.
Starting from the model described in~\cite{Scheibl:1998tk, Blum:2017qnn}, we have obtained in \cite{Bellini:2018epz} a generalised expression for $B_A$
%
%
\begin{equation}\label{eq:master}
B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{\frac{3}{2}(A-1)} \;\;,
\end{equation}
%
%
\noindent which is a function of the spin of the particle $J_A$, its transverse mass $m_{\rm T}$, its size parameter $r_A$ and the source radius $R$. Very importantly, Eq.~\ref{eq:master} takes explicitly into account the source size ($R$), as the coalescence probability naturally decreases for nucleons with similar momenta that are produced far apart in configuration space. 
Moreover, the source size is identified with the  effective sub-volume of the whole system that is governed by the (momentum-dependent) homogeneity length of the interacting nucleons and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry~\cite{Scheibl:1998tk, Blum:2017qnn}. 
Figure~\ref{Fig:BA} shows the source radius dependence of $B_A$ for nuclei and hyper-nuclei with $A = 2, 3$ and 4 whose properties are reported in Tab.~\ref{tab:nucleusradii}. 
For the cases in which more than one estimate for $r_A$ is available, we have adopted the lowest value for the calculations in Fig.~\ref{Fig:BA}.
%
%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.8\textwidth]{coalescenceBA075.eps}
\caption{(Color online) Coalescence parameter $B_A$ as a function of the source radius $R$ as predicted from the coalescence model (Eq.~\ref{eq:master}) for various composite objects with \pt$/A$~=~0.75~\GeVc. For each (hyper-)nucleus, the radius $r$ used for the calculation is reported in the legend.}
\label{Fig:BA}
\end{center}
\end{figure} 
%
%
We observe that the coalescence probability decreases with increasing mass number and $B_A$ decreases with increasing volume. 
For a given $A$, the larger the object radius, the lower is $B_A$, as clearly visible by comparing \hethree~and \hthreelambda. 
For objects with same $A$, mass and spin (e.g. the isobars \tritium~and \hethree), $B_A$ differs only due to the different radius $r_A$. 
This difference is more relevant in small systems, because in large systems the difference between nucleus radii is much smaller than the size of the source.  
Incidentally, this could be experimentally verified with high precision measurements of the production of \tritium~relative to \hethree~in pp collisions. 
The production of objects with radius larger than the source is strongly suppressed, indicating that the process is driven by the lenght scale defined by the object radius relative to the source radius.

@@

\section{Results and discussion} \label{sec:results}
As discussed in the previous sections, the coalescence model describe the coalescence parameter

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.8\textwidth]{B3vsMult073.png}
\caption{(Color online) Coalescence parameter $B_3$ for \hethree~as a function of the average charged particle multiplicity density. The coalescence calculation (continuous black line) is compared to two thermal+blast-wave predictions (dashed lines), obtained by using the Grand Canonical (GC, red)~\cite{Andronic:2017} and Canonical Statistical Model (CSM, blue) \cite{Vovchenko:2018fiy} expectations for the \hethree~yield, respectively. ALICE data from pp (green circles) and \PbPb~(red circles) collisions~\cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015} are reported. }
\label{Fig:3He}
\end{center}
\end{figure}

@@

\newpage
\bibliographystyle{utphysnt} 	
\bibliography{biblio}
\end{document}

>>>>

\subsection{The coalescence approach}
In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963, Kapusta:1980, Scheibl:1998tk}.
The coalescence probability is encoded in the coalescence parameter, $B_{A}$.
Considering that at LHC energies the number of produced protons and neutrons at midrapidity as well as their momentum distributions are expected to be equal, $B_{A}$ is defined as
%
%
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p,n}}\frac{\mathrm{d}^{3}N_{\mathrm{p,n}}}{\mathrm{d}p_{\mathrm{p,n}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.,
\label{eq:BA}
\end{equation}
%
%
where $p_{\mathrm{p,n}}$ are the proton and neutron momenta and $E_{p,n}$ their energies. 
Equation~\ref{eq:BA} represents also the operative definition of $B_A$ that is used by experiments like ALICE to extract the coalescence probability starting from the measured nucleus and nucleon (proton) distributions.
Starting from the model described in~\cite{Scheibl:1998tk, Blum:2017qnn}, we have obtained in \cite{Bellini:2018epz} a generalised expression for $B_A$
%
%
\begin{equation}\label{eq:master}
B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{\frac{3}{2}(A-1)} \;\;,
\end{equation}
%
%
\noindent which is a function of the spin of the particle $J_A$, its transverse mass $m_{\rm T}$, its size parameter $r_A$ and the source radius $R$. Very importantly, Eq.~\ref{eq:master} takes explicitly into account the source size ($R$), as the coalescence probability naturally decreases for nucleons with similar momenta that are produced far apart in configuration space. 
Moreover, the source size is identified with the  effective sub-volume of the whole system that is governed by the (momentum-dependent) homogeneity length of the interacting nucleons and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry~\cite{Scheibl:1998tk, Blum:2017qnn}. 
Figure~\ref{Fig:BA} shows the source radius dependence of $B_A$ for nuclei and hyper-nuclei with $A = 2, 3$ and 4 whose properties are reported in Tab.~\ref{tab:nucleusradii}. 
For the cases in which more than one estimate for $r_A$ is available, we have adopted the lowest value for the calculations in Fig.~\ref{Fig:BA}.
%
%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.8\textwidth]{coalescenceBA075.eps}
\caption{(Color online) Coalescence parameter $B_A$ as a function of the source radius $R$ as predicted from the coalescence model (Eq.~\ref{eq:master}) for various composite objects with \pt$/A$~=~0.75~\GeVc. For each (hyper-)nucleus, the radius $r$ used for the calculation is reported in the legend.}
\label{Fig:BA}
\end{center}
\end{figure} 
%
%
We observe that the coalescence probability decreases with increasing mass number and $B_A$ decreases with increasing volume. 
For a given $A$, the larger the object radius, the lower is $B_A$, as clearly visible by comparing \hethree~and \hthreelambda. 
For objects with same $A$, mass and spin (e.g. the isobars \tritium~and \hethree), $B_A$ differs only due to the different radius $r_A$. 
This difference is more relevant in small systems, because in large systems the difference between nucleus radii is much smaller than the size of the source.  
Incidentally, this could be experimentally verified with high precision measurements of the production of \tritium~relative to \hethree~in pp collisions. 
The production of objects with radius larger than the source is strongly suppressed, indicating that the process is driven by the length scale defined by the object radius relative to the source radius.

@@

\section{Results and discussion} \label{sec:results}
As discussed in the previous sections, the coalescence model provides an analytical expression for $B_A$ as a function of the source size $R$. 
The thermal+blast-wave approach allows us to extract the $B_A$ as a function of the average charged particle multiplicity density, \avdNdeta. Data are also available as a function of multiplicity.
In order to compare models and data, we therefore need to map multiplicity into source radius or viceversa. 
As discussed more extensively in~\cite{Bellini:2018epz}, we perform this mapping based on the parameterisation $R = 0.473 \avdNdeta^{1/3}$. 
The value of the empirical slope parameter is obtained by tuning the parameterisation such that the measured (anti-)deuteron \btwo~in the most central \PbPb~class falls onto the coalescence prediction. In this way, we constrain the coalescence volume with the more differential (anti-)deuteron data and assume that it is the same for all anti- and hyper-nuclei. 
In~\cite{Bellini:2018epz}, we used the parameterisation to map the \avdNdeta~into $R$. Here, we chose to apply the inverse relation and show the comparison between $B_A$ from models and data as a function of the experimentally accessible observable  \avdNdeta. The two choices are equivalent.

We compare $B_A$ as obtained from the coalescence  (Eq.~\ref{eq:master}) and the ther\-mal+\-blast-wa\-ve model approach in Fig.~\ref{Fig:comparison} as a function of \avdNdeta. With respect to~\cite{Bellini:2018epz}, we have extended our study up to $A=4$ \mbox{(hyper-)nuclei}. The available data from ALICE are also reported.

@@

As an example, we have also computed $B_A$ for \hethree~according to the thermal+blast-wave approach for the \pPb~system, by using yield predictions from the Canonical Statistical Model from~\cite{Vovchenko:2018fiy} and the blast-wave parameters from~\cite{Abelev:2013haa}. The result is reported in Fig. \ref{Fig:3He}.

Sigh! To be finished.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.8\textwidth]{B3vsMult073.png}
\caption{(Color online) Coalescence parameter $B_3$ for \hethree~as a function of the average charged particle multiplicity density~\avdNdeta. The coalescence calculation (continuous black line) is compared to two thermal+blast-wave predictions (dashed lines), obtained by using the Grand Canonical (GC, red)~\cite{Andronic:2017} and Canonical Statistical Model (CSM, blue) \cite{Vovchenko:2018fiy} expectations for the \hethree~yield, respectively. ALICE data from pp (green circles) and \PbPb~(red circles) collisions~\cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015} are reported. }
\label{Fig:3He}
\end{center}
\end{figure}

\section{Conclusions}
Sic! To be finished.
\newpage
\bibliographystyle{utphysnt} 	
\bibliography{biblio}
\end{document}
